Computationally Efficient High-Dimensional Regularized Discriminant Analysis

### 2017-01-23 reports/paper-hdrda.Rnw
Cleaned up original RDA's notation.

\cite{Friedman:1989tm} proposed the biased covariance-matrix estimator
\begin{linenomath*}
\begin{align}
    \widehat{\bm \Sigma}_k(\lambda, \gamma) = (1 - \gamma) \widehat{\bm \Sigma}_k(\lambda) + \gamma \frac{\tr\{\widehat{\bm \Sigma}_k(\lambda)\}}{p} \bm I_p,\label{eq:sig-rda}
\end{align}
\end{linenomath*}
where $\gamma \in [0, 1]$ is a regularization parameter that controls the
shrinkage of \eqref{eq:sig-rda} towards $\bm I_p$ and is weighted by the average
of the eigenvalues of \eqref{eq:sig-lambda}. \cite{Friedman:1989tm}
established the RDA classifier by substituting \eqref{eq:sig-rda} into
\eqref{eq:qda}.

Our proposed \emph{HDRDA} classifier yields an
interpretation of the pooling parameter $\lambda$ as discussed above. Moreover,
as we discuss below, our formulation of the \emph{HDRDA} classifier lends itself
to rapid estimation in high-dimensional classification.

@@

Also, notice that if $\alpha_k$ is constant
across the $K$ classes, then $\bm \Gamma_k$ in \eqref{eq:Gamma_k} is independent
of $k$. Consequently, $|\bm \Gamma_k|$ is constant across the $K$ classes and
need not be calculated in \eqref{eq:hdrda-decomposed}.

>>>>

When $\alpha_k = 1 - \gamma$, \eqref{eq:hdrda-cov} resembles the biased covariance-matrix estimator
\begin{linenomath*}
\begin{align}
    \widehat{\bm \Sigma}_k(\lambda, \gamma) = (1 - \gamma) \widehat{\bm \Sigma}_k^{(RDA)}(\lambda) + \gamma \frac{\tr\left\{\widehat{\bm \Sigma}_k^{(RDA)}(\lambda)\right\}}{p} \bm I_p \label{eq:sig-rda}
\end{align}
\end{linenomath*}
employed in the \emph{RDA} classifier, where $\widehat{\bm
  \Sigma}_k^{(RDA)}(\lambda)$ is a pooled estimator of $\bm \Sigma_k$ and
$\gamma \in [0, 1]$ is a regularization parameter that controls the shrinkage of
\eqref{eq:sig-rda} towards $\bm I_p$ weighted by the average of the eigenvalues
of $\widehat{\bm \Sigma}_k^{(RDA)}(\lambda)$. Despite the similarity of
\eqref{eq:sig-rda} to the \emph{HDRDA} covariance-matrix estimator in
\eqref{eq:hdrda-cov}, the \emph{RDA} classifier is impractical for
high-dimensional data because the inverse and determinant of \eqref{eq:sig-rda}
must be calculated when substituted into \eqref{eq:qda}. Furthermore,
\eqref{eq:sig-rda} has no clear interpretation.

@@

Notice that $\bm \Gamma_k$ is singular when $(\lambda, \gamma) = (0, 0)$
because $\bm \Gamma_k = \bm 0_q$, in which case we use the formulation in
\eqref{eq:hdrda-decomposed} instead. Also, notice that if $\alpha_k$ is
constant across the $K$ classes, then $\bm \Gamma_k$ in \eqref{eq:Gamma_k} is
independent of $k$. Consequently, $|\bm \Gamma_k|$ is constant across the $K$
classes and need not be calculated in \eqref{eq:hdrda-decomposed}.
